---
title: 'CSS 205: Final Project'
subtitle: 'Womens Representation in Politics'
author: "Adeline Liem and Harley Clifton"
date: "2025-03-06"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(corrplot)
library(naniar)
library(stargazer)
library(dplyr)
library(lubridate)
library(caret)
library(ROCR)
library(separationplot)
```

# Data Preperation

## Loading the Data

```{r}
# Read in dataset

filepath <- './data/PADD_Agreement_Level_Multiple_Positions.csv'
df <- read_csv(filepath)
```


## Data Cleaning & Wrangling

```{r}
# Create Binary Variables

df$FemSig_Bin <- ifelse(df$FemSig_N > 0, 1, 0)
df$FemNeg_Bin <- ifelse(df$FemNeg_N > 0, 1, 0)
df$FemMed_Bin <- ifelse(df$FemMed_N > 0, 1, 0)
df$FemOb_Bin <- ifelse(df$FemOb_N > 0, 1, 0)

# Creating a New Variable for just Year

df$Dat <- as.Date(df$Dat)
df$year <- year(df$Dat)
```

$~$

# Exploratory Data Analysis

## Number of Observations

```{r}
# Check number of rows with size
nrow(df) # There are 116 total observations

# Check number of distinct countries
n_distinct(df$Con) # 58 different countries
```

```{r}
# Create dataset with number of binary counts for the interested variables
bin_counts <- df %>%
  summarise(
    FemSig_Bin_0 = sum(FemSig_Bin == 0, na.rm = TRUE),
    FemSig_Bin_1 = sum(FemSig_Bin == 1, na.rm = TRUE),
    FemNeg_Bin_0 = sum(FemNeg_Bin == 0, na.rm = TRUE),
    FemNeg_Bin_1 = sum(FemNeg_Bin == 1, na.rm = TRUE),
    FemMed_Bin_0 = sum(FemMed_Bin == 0, na.rm = TRUE),
    FemMed_Bin_1 = sum(FemMed_Bin == 1, na.rm = TRUE),
    FemOb_Bin_0  = sum(FemOb_Bin == 0, na.rm = TRUE),
    FemOb_Bin_1  = sum(FemOb_Bin == 1, na.rm = TRUE)
  )
bin_counts
```


## Plot of the Outcome Variable

*Dependent Variable:* Provisions for Women (`GeWom`): Women, girls, and gender\
“This is a binary variable, taking the value of 1 if any of the peace agreement provisions are specifically addressing women, their inclusion, and their rights. This includes references to girls, widows, mothers, sexual violence (or forms thereof), gender violence, UNSC 1325 or CEDAW, lactating women. If no such provisions are present in the agreement, the value of the variable is 0” (Bell et al. 2021, 24).

```{r}
## Histogram of the Dependent Variable

hist <- ggplot(df, aes(x = GeWom)) + 
  geom_histogram(fill = "pink") +
  labs(title = "Histogram of Dependent Variable  \n Provisions for Women",
       x = "Binary Variable for Provisions for Women  \n (1 = Present/0 = Absent)",
       y = "Frequency") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.title.x = element_text(size = 11),
        axis.title.y = element_text(size = 11))

hist
```
```{r, warning = F}
# Bar graph

bar <- ggplot(df, aes(x = as.factor(GeWom))) + 
  geom_bar(fill = "pink") +
  labs(title = "Histogram of Dependent Variable  \n Provisions for Women",
       x = "Binary Variable for Provisions for Women  \n (1 = Present/0 = Absent)",
       y = "Frequency") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.title.x = element_text(size = 11),
        axis.title.y = element_text(size = 11))

bar
```


## Any Other Interesting Quantities

```{r}
# summary(df)

subs <- df %>% select(GeWom, 
                      FemSig_P, FemNeg_P, FemMed_P, FemOb_P,
                      FemSig_N, FemNeg_N, FemMed_N, FemOb_N,
                      FemSig_Bin, FemNeg_Bin, FemMed_Bin, FemOb_Bin,
                      )

summary(subs)
```


## Plot Missingness in Data

```{r}
# Generate missingness visualization

dat <- df %>% select(GeWom, FemSig_N, FemNeg_N, FemMed_N, FemOb_N)
vis_miss(dat)
```


$~$

# Replicating the Original Model & Findings

## Fit Original Model

```{r}
# Fitting a GLM regression for each category of women in positions of power and provisions for women
sig_b_glm <- glm(GeWom ~ FemSig_Bin, data = df, family = 'binomial')
neg_b_glm <- glm(GeWom ~ FemNeg_Bin, data = df, family = 'binomial')
med_b_glm <- glm(GeWom ~ FemMed_Bin, data = df, family = 'binomial')
ob_b_glm <- glm(GeWom ~ FemOb_Bin, data = df, family = 'binomial')
```


## Regression Table with Model Summary

```{r, warning = F}
# Regression table (Table 5)
stargazer(sig_b_glm, neg_b_glm, med_b_glm, ob_b_glm, type="text",
          covariate.labels = c("Women Signatories", "Women Negotiators", "Women Mediators", "Women Observers"),
          dep.var.caption = "Women Delegates per Negotiation (Binary)",
          dep.var.labels = "Provisions for Women")
```

## Regression Table with Model 1 Alone

```{r, warning = F}
stargazer(sig_b_glm, type="text",
          covariate.labels = c("Women Signatories"),
          dep.var.caption = "Women Delegates per Negotiation (Binary)",
          dep.var.labels = "Provisions for Women")
```



$~$

# Fitting Additional Models

## Model with Signatories and Year

```{r}
year_glm <- glm(GeWom ~ FemSig_Bin + year, 
               data = df, 
               family = 'binomial')
```


## Regression Table with Additional Model Results

```{r, warning = F}
stargazer(year_glm, type="text",
          covariate.labels = c("Women Signatories", "Year"),
          dep.var.caption = "Women Delegates per Negotiation (Binary)",
          dep.var.labels = "Provisions for Women")
```


$~$

# Comparing Models

## Table Comparing Models

```{r, warning = F}
stargazer(sig_b_glm, year_glm, type="text",
          covariate.labels = c("Women Signatories", "Year"),
          dep.var.caption = "Women Delegates per Negotiation (Binary)",
          dep.var.labels = "Provisions for Women")
```


## In-Sample Predictive Performance (AIC/BIC)

```{r}
AIC(sig_b_glm, year_glm)
BIC(sig_b_glm, year_glm)
```


## Out-Of-Sample Predictive Performance (Cross Validation)

```{r}
# Remove missing data from dataframe for cross validation

df_clean <- df[!is.na(df$FemSig_Bin),]
nrow(df_clean)

# Convert to factor
df_clean$GeWom <- as.factor(df_clean$GeWom)
```


```{r}
# Cross validation for the original model (sig_b_glm)

train_control <- trainControl(method = "cv", 
                              number = 10) 

sig_b_glm_cv <- train(GeWom ~ FemSig_Bin, data = df_clean,  
                 method = 'glm', 
                 family = binomial(link = "logit"),
                 trControl = train_control)

sig_b_glm_cv
```
```{r}
# ROC plot for original model
pred1 <- prediction(predict(sig_b_glm_cv, df_clean, type = "prob")[,2], df_clean$GeWom)  
perf1 <- performance(pred1, measure = "tpr", x.measure = "fpr")
plot(perf1, col=rainbow(10))
```

```{r}
# Cross validation for the additional model (year_glm)

train_control <- trainControl(method = "cv", 
                              number = 10) 

year_glm_cv <- train(GeWom ~ FemSig_Bin + year, data = df_clean,  
                 method = 'glm', 
                 family = binomial(link = "logit"),
                 trControl = train_control)

year_glm_cv
```
```{r}
# ROC plot
pred1_year <- prediction(predict(year_glm_cv, df_clean, type = "prob")[,2], df_clean$GeWom)  
perf1_year <- performance(pred1_year, measure = "tpr", x.measure = "fpr")
plot(perf1_year, col=rainbow(10))
```

Based on the analysis above, the additional model year_glm, which predicted GeWom from FemSig_Bin + year, is the best. This is because there is a 67.5% accuracy in the cross validation performance for this model, which is higher than the accuracy of the original model, which was 54.7%. There is also more area under the curve in the ROC plot, indicating a higher amount of true positives.

$~$ 

# Interpreting the Best Model

## Interpret a Coefficient

```{r}

```


## Graph Relationship (with Uncertainty) between chosen Predictor and Outcome

```{r}

```


$~$

# Appendix

### Statement on AI Usage

“I certify that we did not use any LLM or generative AI tool in this assignment”


