---
title: 'CSS 205: Final Project'
subtitle: 'Womens Representation in Politics'
author: "Adeline Liem and Harley Clifton"
date: "2025-03-06"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(corrplot)
library(naniar)
```

# Data Preperation

## Loading the Data

```{r}

```


## Data Cleaning & Wrangling

```{r}

```

$~$

# Exploratory Data Analysis

## Number of Observations

```{r}

```


## Plot of the Outcome Variable

```{r}

```


## Any Other Interesting Quantities

```{r}

```

## Plot Missingness in Data

```{r}

```


$~$

# Replicating the Original Model & Findings

## Fit Original Model

```{r}

```


## Regression Table with Model Summary

```{r}

```


$~$

# Fitting Additional Models

## Model with Different Link Function

```{r}

```


## Model Exploring Interactions

```{r}

```


## Regression Table with Additional Model Results

```{r}

```


$~$

# Comparing Models

## In-Sample Predictive Performance (AIC/BIC)

```{r}

```


## Out-Of-Sample Predictive Performance (Cross Validation)

```{r}

```



Based on the analysis above, _____ model is the best.

$~$ 

# Interpreting the Best Model

## Interpret a Coefficient

```{r}

```


## Graph Relationship (with Uncertainty) between chosen Predictor and Outcome

```{r}

```


$~$

# Appendix

### Statement on AI Usage

“I certify that we did not use any LLM or generative AI tool in this assignment”


