---
title: 'CSS 205: Final Project'
subtitle: 'Womens Representation in Politics'
author: "Adeline Liem and Harley Clifton"
date: "2025-03-06"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(corrplot)
library(naniar)
library(stargazer)
library(dplyr)
```

# Data Preperation

## Loading the Data

```{r}
# Read in dataset

filepath <- './data/PADD_Agreement_Level_Multiple_Positions.csv'
df <- read_csv(filepath)
```


## Data Cleaning & Wrangling

```{r}
# Create Binary Variables

df$FemSig_Bin <- ifelse(df$FemSig_N > 0, 1, 0)
df$FemNeg_Bin <- ifelse(df$FemNeg_N > 0, 1, 0)
df$FemMed_Bin <- ifelse(df$FemMed_N > 0, 1, 0)
df$FemOb_Bin <- ifelse(df$FemOb_N > 0, 1, 0)
```

$~$

# Exploratory Data Analysis

## Number of Observations

```{r}
# Check number of rows with size
nrow(df) # There are 116 total observations

# Check number of distinct countries
n_distinct(df$Con) # 58 different countries
```

```{r}
# Create dataset with number of binary counts for the interested variables
bin_counts <- df %>%
  summarise(
    FemSig_Bin_0 = sum(FemSig_Bin == 0, na.rm = TRUE),
    FemSig_Bin_1 = sum(FemSig_Bin == 1, na.rm = TRUE),
    FemNeg_Bin_0 = sum(FemNeg_Bin == 0, na.rm = TRUE),
    FemNeg_Bin_1 = sum(FemNeg_Bin == 1, na.rm = TRUE),
    FemMed_Bin_0 = sum(FemMed_Bin == 0, na.rm = TRUE),
    FemMed_Bin_1 = sum(FemMed_Bin == 1, na.rm = TRUE),
    FemOb_Bin_0  = sum(FemOb_Bin == 0, na.rm = TRUE),
    FemOb_Bin_1  = sum(FemOb_Bin == 1, na.rm = TRUE)
  )
bin_counts
```


## Plot of the Outcome Variable

*Dependent Variable:* Provisions for Women (`GeWom`): Women, girls, and gender\
“This is a binary variable, taking the value of 1 if any of the peace agreement provisions are specifically addressing women, their inclusion, and their rights. This includes references to girls, widows, mothers, sexual violence (or forms thereof), gender violence, UNSC 1325 or CEDAW, lactating women. If no such provisions are present in the agreement, the value of the variable is 0” (Bell et al. 2021, 24).

```{r}
## Histogram of the Dependent Variable

hist <- ggplot(df, aes(x = GeWom)) + 
  geom_histogram(fill = "pink") +
  labs(title = "Histogram of Dependent Variable  \n Provisions for Women",
       x = "Binary Variable for Provisions for Women  \n (1 = Present/0 = Absent)",
       y = "Frequency") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.title.x = element_text(size = 11),
        axis.title.y = element_text(size = 11))

hist
```


## Any Other Interesting Quantities

```{r}

```


## Plot Missingness in Data

```{r}
# Generate missingness visualization

dat <- df %>% select(GeWom, FemSig_P, FemNeg_P, FemMed_P, FemOb_P)
vis_miss(dat)
```


$~$

# Replicating the Original Model & Findings

## Fit Original Model

```{r}

```


## Regression Table with Model Summary

```{r}

```


$~$

# Fitting Additional Models

## Model with Different Link Function

```{r}

```


## Model Exploring Interactions

```{r}

```


## Regression Table with Additional Model Results

```{r}

```


$~$

# Comparing Models

## In-Sample Predictive Performance (AIC/BIC)

```{r}

```


## Out-Of-Sample Predictive Performance (Cross Validation)

```{r}

```



Based on the analysis above, _____ model is the best.

$~$ 

# Interpreting the Best Model

## Interpret a Coefficient

```{r}

```


## Graph Relationship (with Uncertainty) between chosen Predictor and Outcome

```{r}

```


$~$

# Appendix

### Statement on AI Usage

“I certify that we did not use any LLM or generative AI tool in this assignment”


