---
title: "Women_Representation_Politics"
author: "Adeline Liem & Harley Clifton"
output: html_document
date: "2025-02-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
```

```{r}
# Read in dataset

filepath <- './data/PADD_Agreement_Level_Multiple_Positions.csv'
df <- read_csv(filepath)
df
```



## Histogram of the Dependent Variable

_Dependent Variable:_ `GeWom`: Women, girls, and gender  
“This is a binary variable, taking the value of 1 if any of the peace agreement provisions are specifically addressing women, their inclusion, and their rights. This includes references to girls, widows, mothers, sexual violence (or forms thereof), gender violence, UNSC 1325 or CEDAW, lactating women. If no such provisions are present in the agreement, the value of the variable is 0” (Bell et al. 2021, 24).  

```{r}
# Generate histogram

hist <- ggplot(df, aes(x=GeWom)) + 
  geom_histogram()

hist
```

$~$

## Correlation Matrix

A correlation matrix for the DV and IVs that the original authors included in the model you are replicating.

```{r}


```


$~$

## Data Missingness

A visual or tabular depiction of the missingness in the data from part (2); see p. 251-255 of the text.

```{r}

```

